---
title: 'House Prices: Advanced Regression Techniques'
author: "NYC Data Science Academy"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache = TRUE,
                      warning = FALSE, 
                      message = FALSE,
                      tidy=FALSE,
                      fig.height=6,
                      fig.width=10)


```


## OUTLINE

1. Introduction
2. Loading Data
3. Visualizations
4. Pre-Processing
5. Model Training and Parameter Tuning
6. Variable Importance and Feature selection
7. Summary



## 2. Data Loading & Preparation

### 2.1 Loading data from csv

```{r load_data}
this.dir <- dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(this.dir)
#https://stackoverflow.com/questions/13672720/r-command-for-setting-working-directory-to-source-file-location

## load training data
comp_train <- read.csv("../Data/co_rev_sample_filtered.csv", 
                        header = TRUE, 
                        na.strings = "",
                        stringsAsFactors = FALSE)

comp_train2 = read.csv("../Data/co_rev_sample_filtered_pt2.csv", 
                        header = TRUE, 
                        na.strings = "",
                        stringsAsFactors = FALSE)

comp_train = rbind(comp_train, comp_train2)
rm(comp_train2)

## load test data
# house_test <- read.csv("./test.csv", 
#                         header = TRUE, 
#                         na.strings = "",
#                         stringsAsFactors = FALSE)

str(comp_train)

library(dplyr)
names(comp_train)
```

### 2.2 Getting factor levels from data description

```{r factor_levels}
#not factoring categorical for now

# ## get levels of categorical features from data description
# factorLevel <- list()
# conn <- file("./data_description.txt", open="r")
# f <-readLines(conn)
# for (line in f){
#   if(!grepl("^[[:blank:]]", line) & grepl(": ", line)) {
#     col_name <<- trimws(gsub(":.*", "", line))
#   } else {
#     level <- trimws(gsub("\t.*", "", line))
#     if (level != "") {
#       factorLevel[[col_name]] <- c(factorLevel[[col_name]], level)
#     }
#   }
# }
# close(conn)
# 
# print(factorLevel[1:6])
```

### 2.3 Checking factor levels with data

```{r check_levels}
## check if levels in description cover unique data values
for (varname in names(factorLevel)) {
  levelDiff <- setdiff(unique(house_train[[varname]]), 
                       factorLevel[[varname]])
  if(length(levelDiff)) {
    print(paste(varname, 
                paste(levelDiff, collapse = ", "), 
                sep = ": "))
  }
}

```


### 2.4 Fixing level names

```{r fix_levels}
## fix those levels that don't match with data
## ignore "NA" as they will be considered as missing when converting categorical to factors

unique(house_train$MSZoning)
factorLevel$MSZoning
factorLevel$MSZoning[2] <- "C (all)"

unique(house_train$Neighborhood)
factorLevel$Neighborhood
factorLevel$Neighborhood[13] <- "NAmes"

unique(house_train$BldgType)
factorLevel$BldgType
factorLevel$BldgType[c(2,3,5)] <- c("2fmCon","Duplex","Twnhs")

unique(house_train$Exterior2nd)
factorLevel$Exterior2nd
factorLevel$Exterior2nd[c(17,6,3)] <- c("Wd Shng","CmentBd","Brk Cmn")

## Get levels that only appear in the dataset
for (varname in names(factorLevel)) {
  factorLevel[[varname]] <- intersect(factorLevel[[varname]],
                                      unique(house_train[[varname]]))
}

## Re-run the previous cell to double check
```

### 2.5 Converting column data types

```{r convert_types}
#change to pcts
topct <- function(x) { as.numeric( sub("\\D*([0-9.]+)\\D*","\\1",x) )/100 }
comp_train[['ceo_approval_pct']] = topct(comp_train[['ceo_approval_pct']])

num_cols = c("Quick.paced", "Stressful","Balanced", "Competitive", "Relaxed","Cut.throat")
comp_train[,num_cols] = sapply(comp_train[,num_cols], as.numeric)

#dates: https://stats.idre.ucla.edu/r/faq/how-can-i-format-a-string-containing-a-date-into-r-date-object/
comp_train[['rev_date_num']] = as.Date(comp_train[['review_date']], '%B %d, %Y')

### Case study code:
## convert column datatype to numeric / factor
## On training dataset
# for (varname in names(house_train)[-1]) {
#   if (varname %in% names(factorLevel)) {
#     house_train[[varname]] <- factor(house_train[['MSSubClass']], 
#                                      levels = factorLevel[['MSSubClass']])
#   } else {
#     house_train[[varname]] <- as.numeric(house_train[[varname]])
#   }
# }
# 
# ## On testing dataset
# for (varname in names(house_test)[-1]) {
#   if (varname %in% names(factorLevel)) {
#     house_test[[varname]] <- factor(house_test[[varname]], 
#                                     levels = factorLevel[[varname]])
#   } else {
#     house_test[[varname]] <- as.numeric(house_test[[varname]])
#   }
# }
```

Converting company categories
```{r}
sub = comp_train %>% filter(is.na(Quick.paced), is.na(Slow.paced))
#slow-paced seems like a sparse, useless variable
comp_train$Slow.paced = NULL
sub = comp_train %>% filter(!is.na(Relaxed), !is.na(Cut.throat))
View(sub)


```

Adding date cols:
```{r}
comp_train$month = months(comp_train$rev_date_num)
comp_train$year = format(comp_train$rev_date_num, '%Y')
comp_train$weekday = weekdays(comp_train$rev_date_num)
```


### 2.6 (Optional) Saving data

```{r save_loaded}
comp_train$X <- NULL
rownames(comp_train) <- comp_train$review_id
comp_train$review_id <- NULL
save(comp_train, file = "../Data/co_rev_loaded.RData")
```


## 3. Visualizations

### Loading data (from step 2)

```{r read_loaded}
library(ggplot2)
library(gridExtra)
library(tabplot)
library(lsr)
library(corrplot)
library(dplyr)
library(plotly)

rm(list = ls())
load("../Data/co_rev_loaded.RData")
```




```{r}
numeric_features <- names(comp_train)[sapply(comp_train, is.numeric)]
print(numeric_features)

review_spec_cols = c('agg_rating','comp_ben_rating', 'culture_rating', 'jobsec_advancement_rating', 
       'management_rating', 'work_life_rating', 'helpful_downvote_count',
       'helpful_upvote_count','review_date', 'review_title',
       'reviewer_company_empl_status', 'reviewer_job_location',
       'reviewer_job_title', 'main_text', 'con_text', 'pro_text','rev_date_num')

company_cols = names(comp_train)[!(names(comp_train) %in% review_spec_cols)]

review_spec_numeric = review_spec_cols[review_spec_cols %in% numeric_features]

summary(comp_train)
```

```{r}
company_grp = comp_train %>% 
  group_by(company_name) %>% 
  summarise_if(is.numeric, mean, na.rm = T)

cols = names(company_grp)
cols = cols[c(1:7,10:23)]



tidy_company = melt(company_grp[,cols], id = 'company_name')

co_ratings = tidy_company %>% filter(value >= 1, value <= 5) %>% mutate(mean_individual_rating = mean())

ggplot(co_ratings) + geom_density(aes(x = value)) + facet_wrap(~variable)
  
```


### 3.1 Agg_Rating Histogram

```{r hist_saleprice}
## histogram on SalePrice
g = ggplot(comp_train)
grid.arrange(g + 
               geom_histogram(aes(agg_rating), bins = 5), 
             g + 
               geom_histogram(aes(company_overall_rating), bins = 8), 
             ncol = 2)

 

# ggplotly(ggplot(comp_train) + 
#                geom_histogram(aes(company_overall_rating), bins = 15), 
#              ncol = 2)
```



```{r}
by_co = comp_train %>% 
  filter(year %in% 2016:2017) %>% 
  group_by(company_industry, company_name) %>% 
  summarise_at(numeric_features, mean, na.rm = T)

ggplot(by_co, aes(x = company_overall_rating, y = agg_rating)) + 
  geom_point( position = "jitter") + #could add 'aes(color = company_industry),'
  geom_smooth(method = "lm")
  
```

Histogram of all features
```{r}
compid <- mutate(comp_train[numeric_features], id=as.numeric(rownames(comp_train)))
melt_df = melt(compid, id = 'id')

ggplot(melt_df) + geom_histogram(aes(x = value), bins = 5) + facet_wrap(~variable, scales="free")

```

I want to make it known somehow that the variables below are discrete and so shouldn't be represented by scatter plots.

```{r}

review_numerics = numeric_features[numeric_features %in% review_spec_cols]
to_chart = review_spec_numeric[!grepl("^help",review_spec_numeric)]


library(GGally)
ggp = ggpairs(comp_train[,to_chart],
              lower = list(continuous = 'density'))
ggp

```

Hmm... that looks silly

### 3.2 Plotting all features sorted by SalePrice

```{r table_plot, fig.height=4, fig.width=10}  
## table plot all features on sortded agg_rating
too_many_cats = c('company_hq', 'company_indeed_url', 'ceo_approval_ratings', 'company_count_QnA', 'company_count_jobs',
                  'company_count', 'company_name', 'main_text', 'con_text', 'pro_text', 'review_date', 'review_title',
                 'reviewer_job_location', 'rev_date_num', 'company_count_jobs', 'top_list')

colMtx = names(comp_train)[!(names(comp_train) %in% too_many_cats)]
length(colMtx)

colMtx <- matrix(names(comp_train)[2:length(comp_train)], nrow = 5)
dim(colMtx)

for (i in 1:ncol(colMtx)) {
  tableplot(comp_train, 
            select_string = c(colMtx[,i], "agg_rating"), 
            sortCol = "agg_rating", decreasing = TRUE, 
            nBins = 30)
}
```
Too many outputs. Limiting:
```{r}
colMtx <- matrix(review_numerics, nrow = 4)
dim(colMtx)

for (i in 1:ncol(colMtx)) {
  tableplot(comp_train, 
            select_string = c(colMtx[,i], "agg_rating"), 
            sortCol = "agg_rating", decreasing = TRUE, 
            nBins = 30)
}
```



```{r}

corM = cor(comp_train[to_chart], use = "complete.obs")

corrplot(corM, method = "color", order = "hclust")

```

Heatmappings
```{r}


ggmat = list()
g = ggplot(comp_train)

for (i in 1:length(to_chart)) {
  for (j in 1:length(to_chart)) {
    print(g + geom_bin2d(aes_string(x = to_chart[i], y = to_chart[j]), bins = 4))
  }
}

```

###Through time
```{r}
g = ggplot(comp_train)
g + geom_smooth(aes(x = rev_date_num))





ggdf = comp_train %>% 
  group_by(year, month) %>% 
  filter(year > 2011) %>% 
  summarise(n = n(), agg_rating = mean(agg_rating))

comp_train$weekday <- factor(comp_train$weekday,levels=
                               c('Sunday','Monday','Tuesday','Wednesday','Thursday','Friday','Saturday'))
comp_train$month <- factor(comp_train$month,levels=
                               c('January','February','March','April','May','June','July', 'August', 'September',
                                 'October', 'November', 'December'))


# http://www.sthda.com/english/wiki/ggplot2-line-plot-quick-start-guide-r-software-and-data-visualization

ggdf$month = factor(ggdf$month,levels=
                               c('January','February','March','April','May','June','July', 'August', 'September',
                                 'October', 'November', 'December'))
  
ggdf2 = comp_train %>% 
  filter(year>2011) %>% 
  group_by(weekday, year) %>% 
  summarise(n = n(), agg_rating = mean(agg_rating))

library(RColorBrewer)


ggplot(ggdf2, aes(x=weekday, y= n, ,group= year, color = year)) +
  geom_line() +
  geom_point() + scale_color_brewer(palette = 'PuBu') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + ggtitle("Reviews by Weekday") 

ggplot(ggdf2, aes(x=weekday, y= agg_rating, ,group= year, color = year)) +
  geom_line() +
  geom_point() + scale_color_brewer(palette = 'PuBu') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + ggtitle("Reviews by Weekday") 



ggplot(ggdf, aes(x=month, y= n, group= year, color = year)) +
  geom_line() +
  geom_point() + scale_color_brewer(palette = 'PuBu') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + ggtitle("Reviews by Month") 
  
ggplot(ggdf, aes(x=month, y= agg_rating, group= year, color = year)) +
  geom_line() +
  geom_point() + scale_color_brewer(palette = 'PuBu') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + ggtitle("Reviews by Month")  



```

```{r}
#https://www.r-bloggers.com/plot-weekly-or-monthly-totals-in-r/
comp_train$Month <- as.Date(cut(comp_train$rev_date_num,
  breaks = "month"))
comp_train$Week <- as.Date(cut(comp_train$rev_date_num,
  breaks = "week",
  start.on.monday = FALSE)) 

# graph by month:
ggplot(data = comp_train,
  aes(Month, agg_rating)) +
  stat_summary(fun.y = mean, # adds up all observations for the week
    geom = "line") + # or "line"
  scale_x_date(
    date_labels = "%Y-%m",
    date_breaks = "3 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # custom x-axis labels


# graph by week:
ggplot(data = comp_train,
  aes(Week, agg_rating)) +
  stat_summary(fun.y = mean, # adds up all observations for the week
    geom = "line") + # or "line"
  scale_x_date(
    date_labels = "%Y-%m-%d",
    date_breaks = "1 week") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # custom x-axis labels



```


```{r}
ggplot(ggdf2, aes(x=weekday, y= agg_rating/n,group= year, color = year)) +
  geom_line() +
  geom_point() + scale_color_brewer(palette = 'Blues') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + ggtitle("Mean Rating by Weekday")

ggplotly(ggplot(ggdf, aes(x=month, y= agg_rating/n ,group= year, color = year)) +
  geom_line() +
  geom_point() + scale_color_brewer(palette = 'Blues') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + ggtitle("Mean Rating by Month")
  )



```


Need to drill down to a story or two. Extra graphics here if need be: https://stats.stackexchange.com/questions/133450/visualization-and-overplotting-alternative-to-scatters

Count by indsutry
```{r}
g = ggplot(comp_train %>% 
  group_by(company_industry) %>% 
  summarise(n = n()) %>% arrange(desc(n))) +
  geom_bar(aes(x = reorder(company_industry,-n), y = n), stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 45, hjust = 3))
ggplotly(g)

```

Plotting ratings through time by industry
```{r}
company_agg = comp_train %>% 
  filter(year>2011) %>% 
  group_by(year,company_industry) %>% 
  summarise(n = n(), agg_rating = mean(agg_rating))

# company_agg$date = as.Date(paste(company_agg$year, company_agg$month, '01', sep = '-'), format = '%Y-%B-%d')

company_agg = company_agg[complete.cases(company_agg),]

top_inds = comp_train %>% 
  group_by(company_industry) %>% 
  summarise(n = n()) %>% arrange(desc(n)) 
top_inds = top_inds[1:10,'company_industry']

ggplot(data = company_agg %>% filter(company_industry %in% top_inds$company_industry)) +
  geom_line(aes(year, agg_rating, color = company_industry, group = company_industry)) +
  ggtitle("Top 10 Industries") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # custom x-axis labels

ggplot(data = company_agg %>% filter(company_industry %in% top_inds$company_industry),
  aes(year, n)) +
  geom_line(aes(group = company_industry, color = company_industry))

```

```{r}
#best and worst companies:
byco_rev = comp_train %>% 
  filter(year>2016) %>% 
  group_by(company_name) %>% 
  summarise(n = n(), mean_agg_rating = mean(agg_rating), company_wide_rating = mean(company_overall_rating))

top10 = byco_rev %>% filter(n > 100) %>% top_n(10, mean_agg_rating)
bot10 = byco_rev %>% filter(n > 100) %>% top_n(10, -mean_agg_rating)

ggplotly(
  ggplot(top10, aes(x = reorder(company_name, -mean_agg_rating), y = mean_agg_rating)) + 
    geom_bar(stat = 'identity') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
)

ggplotly(
  ggplot(bot10, aes(x = reorder(company_name, -mean_agg_rating), y = mean_agg_rating)) + 
    geom_bar(stat = 'identity') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
)

```

